Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-17 paper/sections/proof-reconstruction.tex
[ paper ] minor fix.

In this section, we emulate each \Metis inference rule by proving a
function with the same name, and a theorem that
proves the soundness of the function. Then, we will find
the following pattern to present the formalization for
the \Metis inference rules. The function name written in bold print is a \Metis
inference rule in \TSTP derivation. The same function name written
in italics refers to the emulated version presents in this section.
Each emulated version states a theorem to prove the soundness of the rule.
This theorem is named by using the prefix \emph{thm}
and the name of the rule.

@@

\begin{remark}
Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
with the \simplify rule in \TSTP derivations, we choose a different option.
In the translation from \TSTP to \Agda, we take the list of derivations
and use a classical left folding ($foldl$) with $simplify$ and the list with
$φ₁, φ₂, \cdots, φₙ$. That avoids us to define a new sequent type to
support \List \Prop type in the conclusion side.
\end{remark}

>>>>

In this section, we emulate each \Metis inference rule by proving a
function with the same name, and a associated theorem.
The following pattern is used to present the formalization.
The function name written in bold print
is a \Metis inference rule in \TSTP derivations.
The same function name written in italics refers to its emulated
version.
Each emulated rule states a theorem to prove its soundness.
This theorem is named by using the prefix \emph{thm}
and the name of the rule.

@@

\begin{remark}
Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
with the \simplify rule in \TSTP derivations, we choose a different
option. In the translation from \TSTP to \Agda, we take the list of
derivations and use a classical left folding ($foldl$) with
$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$.
That avoids us to define a new sequent type to
support \List \Prop type in the conclusion side.
\end{remark}
